\chapter{Conclusions}
\label{ch:conclusions}
In this thesis we propose three deep learning based approaches to make person search applicable to real-world applications. For the video-based person search, we employ a diversity regularized spatial attention model to detect similar local patches across multiple video frames. This method determines whether a particular part of the body is occluded or not and align corresponding image patches across frames.
On the other hand, we collect a large-scale person description dataset. A recurrent neural network with gated neural attention is proposed to learn the affinities between the query sentence and person images. We extend the natural language based person search to the general visual-semantic matching problem. A cross-model cross-entropy loss function and a co-attention model are designed to solve the visual-semantic matching. The two-stage framework achieves accuracy and efficiency simultaneously.
%The semantic attention model avoids the weaknesses of RNNs and generates better textual features. 

Despite our efforts toward person search, the methods developed can be applied to other vision tasks as well. The multiple spatial attention and diversity regularization can be used for fine-grained classification; the cross-model cross-entropy loss is suitable for cross-domain feature learning; the method for textual-visual matching is also compatible with language and vision-related tasks such as image captioning and visual question and answering. Person search is far from being solved, more cues and techniques such as social relationship and whole scene images are also worth to be investigated.