\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\markboth{\uppercase{Acknowledgments}}{\uppercase{Acknowledgments}}

I am really fortunate to be supervised by Prof. Xiaogang Wang, an absolutely devoted advisor, who gradually cultivates my ability to conduct in-depth research. He is a person with great aptitude, diligence, and persistence, who inspires me to work harder and think deeper. Without his help, I would never have published so many papers.

I was really lucky to work with so many talented people during my M.Phil. period. I would like to thank Hongsheng Li, Wanli Ouyang, Dahua Lin, Change (Cavan) Loy, and Xiaoou Tang. Their insightful suggestions and research attitude encourage me to conduct in-depth reflection for not only my research but also my life.

I must appreciate my colleague Tong Xiao, Wei Yang, Kai Kang, Jing Shao, Xiao Chu, Yantao Shen, Lu Sheng, Rui Zhao, Xingyu Zeng, Shuai Yi, Zhuoyi Zhao, Hongyang Li, Shuai Li, Kun Wang, Xihui Liu, Yixiao Ge, Hang Zhou, Peng Gao, Xiaoyang Guo, Yonglong Tian, Yuanjun Xiong, and Ruihui Wang. Thank all of my colleagues for supporting me so much during my study at The Chinese University of Hong Kong.

I would like to thank Leonid Sigal, Peter Carr, and Slawomir Bak, for offering me the great opportunity to work at Disney Research; Liang Lin, Zhe Lin, Xiaohui Shen, Brian Price, Bolei Zhou, Dayu Yue, Jiayun Wang, Junting Pan and Peter Mathews, for providing valuable suggestions during our collaborations; and Antonio Torralba and Huchuan Lu, for supporting and encouraging me to pursue my career aspiration as a professor.

Last but not least, my deepest gratitude to my parents, who tought me right from wrong and would always be there for me.